Multiset-trie data structure

### 2018-11-13 tex/tex/s_experiments.tex
Paper updates (introduction, experiments)

%
This section contains results of experiments that were performed on the multiset-trie 
data structure. The implementation of multiset-trie is done in the \CC 
{ programming} language. The current implementation uses only the standard 
library of \CC14 version of the standard and has a command line interface. The implementation 
of the program was optimized for testing and therefore, the program operates 
with files, in order to process queries. After processing all the queries 
the results are stored in files for further analysis.

In our experiments we will test the functions: \textsc{submsetExistence}, 
\textsc{supermsetExistence}, \textsc{getAllSubmsets} and 
\textsc{getAllSupermsets}. Performance of the functions will be measured by 
the number of visited nodes in multiset-trie by the particular function. In 
particular the performance is inversely proportional to the number of visited 
nodes.

@@

The selected parameters of the data structure that will be varied in experiments 
are as follows:
%
\begin{itemize}
\item $\sigma$ - the cardinality of the alphabet $\Sigma;$
%
\item $n$ - the maximal degree of a node, which explicitly defines the maximal 
multiplicity of elements in a multiset;
%
\item $\phi$ - mapping of letters from $\Sigma$ into a set of consecutive 
integers;
%
\item $d$ - density of a multiset-trie.
%
\end{itemize}
The cardinality of a power multiset $N$ is equal to $n^\sigma,$ which means that 
density $d$ of a multiset-trie depends on parameters $|M|,$ $\sigma$ and $n.$ 
Because parameters $\sigma$ and $n$ are set when a multiset-trie is initialized, 
the parameter $|M|$ will be varied to change the density in experiments. As we 
mentioned in Chapter~\ref{c:description}, the mapping $\phi$ determines the 
correspondence of letters to levels in multiset-trie, i.e. it defines the ordering of 
levels in multiset-trie. It is also true, that $\phi$ defines the ordering in multisets.

% anouncement of the experiments
In the next sections we will present the behavior of the multiset-trie data 
structure depending on the selected parameters as well as the benchmark 
of the multiset-trie against trie and hash map data structures. 
% outline of the experiment section
We start with experiments that are performed on an artificially generated data in 
order to give a general picture of the multiset-trie performance. In the 
Experiment~\hyperref[s:exp1]{1} a special case of the multiset-trie is considered. 
Only sets are allowed to be stored in the data structure, i.e. the maximal allowed 
multiplicity is set to 1. The performance is measured with respect to the density 
of the multiset-trie.
%
The Experiment~\hyperref[s:exp2]{2} is an extension of the previous one. Here, 
we also measure the performance of the multiset-trie depending on its density. 
The difference is that the allowed multiplicity of an element is raised, i.e. 
multisets are allowed to be stored in the data structure. 
%
Summarizing the tests of performance depending on the density we present the 
Experiment~\hyperref[s:exp3]{3}. It shows a non linearity of the performance 
with respect to the density of the multiset-trie.
%
The next experiment on the multiset-trie uses the real world data. In 
Experiment~\hyperref[s:exp4]{4} the influence of the mapping $\phi$ is studied. 
The input data is obtained by mapping of the real words from English dictionary 
to the set of consecutive integers using the function $\phi.$ The experiment 
shows that the performance of the multiset-trie can be noticeably optimized using 
different mappings $\phi.$ It also shows the usability of the multiset-trie in terms 
of real data demonstrating the high performance of search queries.
%
After all the experiments we present an empirical comparison of multiset-trie 
data structure with inverted index. Inverted index is considered in two versions, 
when it uses trie and hash map for storing multisets. In the comparison we use 
two types of queries exact retrieval and searching for the first submultiset.

\paragraph*{Data generation}
We denote by \emph{input data} the data that is inserted into multiset-trie and 
by \emph{test data} the data which will be used for queries in order to test the 
performance of the functions.

@@

\subsection{Experiment 5} \label{s:exp5}
In this experiment we demonstrate the performance of multiset-trie data structure 
compared to inverted index. The data structures that were used for inverted index 
implementation are trie and hash map. Both indexes were implemented in~\CC{ to} 
avoid any optimization or degradation of performance caused by different programming 
language implementation.

During tests all three data structures used the same interface for benchmark that operates 
with files as its input and output. Each data structure was loaded with the same input data 
and was queried with the same test data. The input data consists of multisets that are 
generated at random with respect to $\sigma = 15$ and $n = 3.$ All together the input dataset 
has 300000 randomly generated multisets. The test dataset was constructed with the same 
$\sigma$ and $n$ having cardinality 100000 multisets.

First, we present the results of performing an exact search query on each data structure. 
The results on figure~\ref{fig:e5ex} show that hash map performs the best, which is not 
surprising, since its access complexity is $O(1).$ However, note that performance of 
multiset-trie does not depend on the multiset being searched. The trie version of the 
inverted index performs the worst in this experiment, because its performance is dependent 
on the multiset size.

\begin{figure}
\center
\includegraphics[width=.4\textwidth]{exact.pdf}
\caption{Experiment 5, exact search.}
\label{fig:e5ex}
\end{figure}

The results of the submultiset query are presented on figure~\ref{fig:e5subm}. Here, each searching 
query was terminated either when the first submultiset is found or all potential submultisets were 
checked for submultiset inclusion. Multiset-trie outperforms both trie and hash map inverted 
indexes by a major factor due to its design. Multiset-trie operates multiplicities on a node level 
while trie does it on a tree level. In the trie one should traverse the tree in order to see if the element 
of some multiplicity is inside, while in multiset-trie one just has to check if the node has appropriate 
child. In the case of hash map we can operate on as low as the whole multiset level, which is of course 
inconvenient when it comes to multiset containment queries.

Note that multiset-trie is sparse in this experiment, however, the multisets that do not satisfy the query 
are discarded much quicker than in trie or hash map.

\begin{figure}
\center
\includegraphics[width=.4\textwidth]{submset.pdf}
\caption{Experiment 5, first submultiset search.}
\label{fig:e5subm}
\end{figure}

>>>>

%
This section contains results of experiments that were performed on the multiset-trie 
data structure. In particular, we will test the functions: \textsc{submsetExistence}, 
\textsc{supermsetExistence}, \textsc{getAllSubmsets} and 
\textsc{getAllSupermsets}.

The implementation of multiset-trie is done in the \CC 
{ programming} language. The current implementation uses only the standard 
library of \CC14 version of the standard and has a command line interface. The implementation 
of the program was optimized for testing and therefore, the program operates 
with files, in order to process queries. After processing all the queries 
the results are stored in files for further analysis.

%Performance of the functions will be measured by 
%the number of visited nodes in multiset-trie by the particular function. In 
%particular the performance is inversely proportional to the number of visited 
%nodes.

@@

The selected parameters of the data structure that will be varied in experiments 
are as follows:
%
\begin{itemize}
\item $\sigma$ - the cardinality of the alphabet $\Sigma;$
%
\item $n$ - the maximal degree of a node, which explicitly defines the maximal 
multiplicity of elements in a multiset;
%
\item $\phi$ - mapping of letters from $\Sigma$ into a set of consecutive 
integers;
%
\item $d$ - density of a multiset-trie.
%
\end{itemize}
The cardinality of a power multiset $N$ is equal to $n^\sigma,$ which means that 
density $d$ of a multiset-trie depends on parameters $|M|,$ $\sigma$ and $n.$ 
Because parameters $\sigma$ and $n$ are set when a multiset-trie is initialized, 
the parameter $|M|$ will be varied to change the density in experiments. As we 
mentioned in Section~\ref{c:description}, the mapping $\phi$ determines the 
correspondence of letters to levels in multiset-trie, i.e. it defines the ordering of 
levels in multiset-trie. It is also true, that $\phi$ defines the ordering in multisets.

% anouncement of the experiments
In the next sections we will present the behavior of the multiset-trie data 
structure depending on the selected parameters as well as the comparative 
benchmark of the multiset-trie against B+ tree implementation of inverted index. 
% outline of the experiment section
We start with experiments that are performed on an artificially generated data in 
order to give a general picture of the multiset-trie performance. In the 
Experiment~\hyperref[s:exp1]{1} a special case of the multiset-trie is considered. 
Only sets are allowed to be stored in the data structure, i.e. the maximal allowed 
multiplicity is set to 1. The performance is measured with respect to the density 
of the multiset-trie.
%
The Experiment~\hyperref[s:exp2]{2} is an extension of the previous one. Here, 
we also measure the performance of the multiset-trie depending on its density. 
The difference is that the allowed multiplicity of an element is raised, i.e. 
the data structure is populated with multisets. 
%
Summarizing the tests of performance depending on the density we present the 
Experiment~\hyperref[s:exp3]{3}. It shows a non linearity of the performance 
with respect to the density of the multiset-trie.
%
The next experiment on the multiset-trie uses the real world data. In 
Experiment~\hyperref[s:exp4]{4} the influence of the mapping $\phi$ is studied. 
The input data is obtained by mapping of the real words from English dictionary 
to the set of consecutive integers using the function $\phi.$ The experiment 
shows that the performance of the multiset-trie is noticeably influenced by 
different mappings $\phi.$ It also shows the usability of the multiset-trie in terms 
of real data demonstrating the high performance of search queries.
%
After all the experiments we present an empirical comparison of multiset-trie 
data structure with B+ tree based inverted index. We use inverted index 
to store and retrieve multisets in the same way as it is described in the paper by 
Helmer and Moerkotte~\cite{Helmer2003} for sets. In the comparison we use 
three types of queries exact, submultiset and supermultiset retrieval.

\subsection*{Data generation}
We denote by \emph{input data} the data that is used to fill the structure prior 
to testing and by \emph{test data} the set of queries that is used to test the 
performance of the functions.

@@

\subsection{Experiment 5} \label{s:exp5}
In this experiment we demonstrate the performance of multiset-trie data structure 
compared to B+ tree based inverted index. The data structure is also implemented 
in~\CC{ to} avoid any optimization or degradation of performance caused by different 
programming language implementation.

During tests both data structures used the same interface for benchmark that operates 
with files as its input and output. Each data structure was loaded with the same input data 
and was queried with the same test data. The input and test data were generated artificially 
according to parameters $\sigma$ and $n.$ The combinations of parameters is as follows in the 
Table~\ref{t:benchmark}.

\begin{table}[h]
\center
\begin{tabular}{|c|c|}
\hline
$\sigma$ & $n$ \\
\hline
5		& 1\\
\hline
30	& 1 \\
\hline
5		& 3 \\
\hline
15	& 3 \\
\hline
30	& 3 \\
\hline
10	& 10 \\
\hline
\end{tabular}
\caption{Configuration of $\sigma$ and $n$ in benchmark.}
\label{t:benchmark}
\end{table}

We tested all the three types of query on all of the configurations from the Table~\ref{t:benchmark} which 
results in 18 experiments total, i.e. 6 experiments per query type. In each of the experiment we measured an 
average time consumed by the data structure to process the query.

The results of the exact search, submultiset search and supermultiset search experiments are shown in the tables 
Table~\ref{t:res_ex}, Table~\ref{t:res_sub} and Table~\ref{t:res_sup} respectively .

\begin{table}[h]
\center
\begin{tabular}{|c|c|c|c|}
\hline
$\sigma$ & $n$ & Multiset-trie ($\mu s$) & Inverted index ($\mu s$) \\
\hline
5		& 1 & 3.45 & 17782.35\\
\hline
30	& 1 & 4.18 & 24865.93\\
\hline
5		& 3 & 2.20 & 1508.81\\
\hline
15	& 3 & 4.39 & 2146.36\\
\hline
30	& 3 & 10.67 & 3639.97\\
\hline
10	& 10 & 6.93 & 384.05\\
\hline
\end{tabular}
\caption{Exact search.}
\label{t:res_ex}
\end{table}

\begin{table}[h]
\center
\begin{tabular}{|c|c|c|c|}
\hline
$\sigma$ & $n$ & Multiset-trie ($\mu s$) & Inverted index ($\mu s$) \\
\hline
5		& 1			& 8.96 & 73500.84\\
\hline
30	& 1			& 17.33 & 547572.74\\
\hline
5		& 3			& 117.95 & 162360.43\\
\hline
15	& 3			& 20.74 & 443321.39\\
\hline
30	& 3 		& 23.75 & 947706.14\\
\hline
10	& 10		& 55.59 & 466022.68\\
\hline
\end{tabular}
\caption{Submultiset search.}
\label{t:res_sub}
\end{table}

\begin{table}[h]
\center
\begin{tabular}{|c|c|c|c|}
\hline
$\sigma$ & $n$ & Multiset-trie ($\mu s$) & Inverted index ($\mu s$)\\
\hline
5		& 1 		& 10.63 & 63073.86\\
\hline
30	& 1 		& 14.65 & 449251.68\\
\hline
5		& 3 		& 171.04 & 163256.77\\
\hline
15	& 3 		& 43.42 & 425733.80\\
\hline
30	& 3 		& 22.06 & 729831.34\\
\hline
10	& 10 	& 58.32 & 373784.81\\
\hline
\end{tabular}
\caption{Supermultiset search.}
\label{t:res_sup}
\end{table}

We can see that multiset-trie outperforms inverted index in all of the experiments by up to 4 orders of magnitude. 
In exact search multiset-trie has to traverse only up to $\sigma+1$ nodes in order to get query result. It is seen 
from results that with increase of $\sigma$ the processing time for multiset-tire also increases. Interestingly, the 
multiplicity also affects the time of processing, however, this happens passively. Multiplicity or degree of a node $n$ 
defines what multisets can be stored in multiset-trie. Thus, it affects the structure and density of the multiset-trie.

As for the inverted index, it must fetch all the postings according to each element in a test multiset and then intersect 
the results in order to answer the query. This is a more time consuming operation than a simple tree traversal, which we 
can see from results. Postings are of course filtered on-the-fly to reduce the cost of intersection, however these are still 
additional operations to be performed. Note, that inverted file will also access at most $\sigma$ postings during search, 
but in addition to access some extra processing is required.

The submultiset and supermultiset basically do not change to much in the case of inverted file, because the algorithm consists 
of the same steps: the postings are fetched according to elements of the test multiset, then they are filtered on-the-fly 
according to the query type, and at the end the postings either has to be united or intersected. So, besides a traversal of at most 
$\sigma$ keys of the index additional processing is required. Note, that every key is mapped to a list of postings which 
can be large as index grows.

In the case of multiset-trie only a traversal of the tree is required which is much faster than processing of postings as we can 
see from results. In the worst case the whole tree is traversed, but so is for inverted file.

### 2018-11-13 tex/tex/s_intro.tex
algorithms adjusted and get-all algorithms added
Paper updates (introduction, experiments)

\section{Introduction} \label{c:introduction}
[Will be rewritten]
%
% some intro
During recent years the popularity of digital data has increased. All sorts of 
information such as text, audio and video can now be accessed by searching 
\emph{information retrieval systems}. Information retrieval (IR) is the science of 
searching information units in a collection of data. Most commonly IR systems 
are used for searching a text-based content such as text documents in a database. 
Such IR systems are called \emph{full-text search systems}.

Full-text search techniques can be applied directly on the database. However, 
it is a very expensive procedure in terms of running time complexity, because it 
requires a frequent accesses to the database. In order to reduce this number, indexes 
were invented. Indexes narrow down the search using pre-generated meta data 
constructed from the data in the database. Furthermore the meta data can be 
organized in a data structure that would provide fast retrieval of data according 
to search queries.

In IR most systems use the concept of an inverted index to achieve full-text 
indexing of a database. Inverted index consists of two parts: \emph{postings} 
and \emph{dictionary}, a search structure that is used to locate a specific entries 
in a posting. A posting entry can be created on different levels depending on data 
that needs to be indexed. Most common for full-text indexes are document level 
entries. In this context a posting is defined to be a list of identifiers or keys that are 
further used to locate a specific document in the database \cite{zobel1992efficient}.

An index is a search structure that is used to process user queries. The query 
can be processed in different ways according to the \emph{retrieval model}. The 
retrieval model that will be discussed in the thesis is the \emph{boolean retrieval 
model} that views each document in a database as a set of words. The document 
itself is an information unit a retrieval system is built over. In our case an 
information unit is defined to be a textual document.

The boolean retrieval model is based on set and multiset theory together with 
boolean algebra. \emph{Set and multiset containment operations} are used to 
derive the similarities between objects, and consequently make decisions on their 
association. Thus, the multiset containment operations allow us to 
search objects not only with exact queries but also to retrieve the most relevant 
set of results that satisfy a given search query \cite{baeza1999modern,manning2008introduction,zobel2006inverted}.

% research topic
% walking through the new terms and so on
% brief overview of the literature (relations to other work etc.)
%

The dictionary (search structure) of the inverted index can be organized in different ways in 
order to meet the required types of queries and specification of data. For example, 
it can be organized as a search tree, hash map, array, heap, linked list, etc. In our 
research we will be focused on search trees. The most efficient search tree index 
nowadays is the Generalized Search Tree (GiST). Its flexibility stems from combining 
functionality of B+-trees, R-trees and RD-trees. GiST further extends their functionality 
providing support for a variety of data types together with the nearest-neighbor 
search \cite{broder2006indexing,hellerstein1995generalized,kornacker1999high}.

% description of innovations
%
The proposed data structure \emph{multiset-trie} can be used as an alternative 
implementation of the search structure in an inverted index. It is an extension of 
the \emph{set-trie} data structure proposed by Savnik \cite{savnik2013index}. 
Set-trie is a trie based data structure that is used for storing and fast retrieval of 
objects represented as sets. The set-trie provides the nearest-neighbor search by 
implementing methods that perform set-containment queries. Multiset-trie extends 
the abilities of set-trie and provides support for storing and retrieving objects 
that can be represented as both sets and multisets. It also implements 
multiset-containment methods together with the basic tree methods such as search, 
deletion and insertion.

The multiset-trie is an $n$-ary tree based data structure with properties similar to 
those of a trie. 
This particular combination allows us to associate multisets with a collection 
of nodes in a tree. Every node represents a symbol with particular multiplicity. 
%
Multiset-trie is a kind of search tree. Similarly to a trie, it uses common prefixes 
to narrow down the search. Unlike the compact prefix tree, Patricia, the multiset-trie 
does not provide the ability to compress a path. However, the absence of path 
compression makes the multiset-trie a perfectly height-balanced tree.

The multiset-trie is designed for efficient execution of the multiset containment 
operations. In particular, it supports the operations \textsc{submsetExistence}, 
\textsc{supermsetExistence}, \textsc{getAllSubmsets} and \textsc{getAllSupermsets}. 
The so-called "existence" queries implement the nearest-neighbor search queries. The 
functions \textsc{submsetExistence} and \textsc{supermsetExistence} search for 
the closest submultiset and supermultiset in the multiset-trie respectively and return 
an answer whether such a multiset exists in the data structure. The so-called 
"getAll" functions act in the same way as "existence" functions, but they do not 
terminate once they have reached the desired multiset. Alternatively, these functions 
store the results and continue until all the multisets that satisfy the query are retrieved.

% paper organization
%
Let us now present the organization of the thesis. 
In the following Chapter~\ref{c:description} we present the description of the 
multiset-trie data structure. The representation of multisets in multiset-trie is 
explained in detail. The organization of the data structure is also presented 
graphically.
%
In Chapter~\ref{c:operations} we present operations that multiset-trie currently 
supports. The multiset containment functions \textsc{submsetExistence}, 
\textsc{supermsetExistence}, \textsc{getAllSubmsets} and \textsc{getAllSupermsets} 
are presented together with the basic search tree functions such as \textsc{insert}, 
\textsc{delete} and \textsc{search}. The algorithms in pseudo code are presented 
as well. 
%
The description of multiset-trie functions and procedures is followed by the 
mathematical analysis of their complexity in Chapter~\ref{c:analysis}. 
In this analysis, we make an assumption that multisets are constructed uniformly at 
random and are parametrized by several parameters, such as multiplicity and the alphabet 
$\Sigma.$ By using probabilistic tools we describe time complexity of the algorithms 
and space complexity of the structure.
%
Further, in Chapter~\ref{c:experiments} we present an empirical study of the 
multiset-trie. Artificially generated as well as real-world data sets are used in experiments. 
The experiments are dedicated to testing the performance of the data structure while 
varying selected parameters. The experiments also show some methods for 
optimizing a multiset-trie.
%
The Chapter~\ref{c:relwork} presents related work. The connection to the set-trie 
data structure \cite{savnik2013index} is discussed more explicitly. We also relate 
the multiset-trie to the information retrieval systems. In particular, we refer to the 
inverted index data structure and discuss how the multiset-trie can be used as a 
database index.
%
Finally, in Chapter~\ref{c:conclusions} our conclusion about the multiset-trie 
data structure and discussion of future work are presented.

>>>>

\section{Introduction} \label{c:introduction}
%
% some intro
During recent years the popularity of digital data has increased. Huge amount of diverse data is collected in databases and 
processed regularly. Data processing usually consists of operations such as filtering, sorting and aggregation. This requires 
indexing for optimization of data processing especially when it is repetitive. Data often includes duplicates or multivalued 
attributes that are complicated to process efficiently when sophisticated queries are required.

Multisets or bags are not well supported by storage systems for processing. Usually multisets have to be stored in a 
simpler format that does not allow a direct analysis of the data. Such storage results in a more complex processing, 
since multisets have to be re-constructed or pre-processed first in order to run the query. It also becomes impossible
to execute containment queries on multisets.

Currently the most efficient ways for multisets storage and processing involve inverted files, signature trees and B+ tree.
Such solutions provide key-value look-up only, which does not allow to perform containment queries on multisets directly and efficiently.
Additional processing is required such as intersection or union of obtained partial results from key-value look-ups. The post 
processing of partial results can be optimized, however, it is still not as efficient and usually requires additional encoded 
signatures or other types of identifiers to speed-up the process.

% --------------------------------------------------------------------------------------------------------------------------------------------------------------------

% description of innovations
%
In this paper we propose a data structure \emph{multiset-trie} that is designed for storage and processing of multisets.
It is an extension of the \emph{set-trie} data structure proposed by Savnik \cite{savnik2013index}. 
Set-trie is a trie based data structure that is used for storing and fast retrieval of 
objects represented as sets. The set-trie provides the nearest-neighbor search by 
implementing methods that perform set-containment queries. Multiset-trie generalizes 
set-trie and provides support for storing and retrieving objects that can be represented 
as both sets and multisets.

The multiset-trie is an $n$-ary tree based data structure with properties similar to those of a trie. 
This particular combination allows us to associate multisets with a collection of nodes in a tree. 
Every node represents an element of a multiset with particular multiplicity. 
%
Multiset-trie is a kind of search tree. Similarly to a trie, it uses common prefixes 
to narrow down the search. It also implements the basic tree methods such as 
search, deletion and insertion. Unlike the compact prefix tree, Patricia, the multiset-trie 
does not provide the ability to compress a path. However, the absence of path 
compression makes the multiset-trie a perfectly height-balanced tree.

The multiset-trie is designed for efficient execution of the multiset containment 
operations. It handles multisets directly by having access to each of the element 
without the need to reconstruct them for processing, which allows fast retrieval and 
containment queries. In particular, it supports submultiset and supermultiset queries.
The operations allow to find and retrieve the closest submultisets or supermultisets 
as well as to find and retrieve all of them.
%
Since multiset is a generalized version of sets that allows duplicates multiset-trie can be 
used for storing and processing sets supporting the same set of operations and providing 
the same efficiency.

% --------------------------------------------------------------------------------------------------------------------------------------------------------------------

% key results
Empirical studies on real data show, that multiset-trie is sensitive to the context, which can 
be further used to optimize data structure for particular data. Moreover, knowing the data 
it is possible to estimate the overall performance of the multiset-trie both time and space 
related using our mathematical theory that describes multiset-trie.
%
The comparative study shows how efficient multiset-trie is by outperforming inverted file in 
both exact and containment queries by up to 4 orders of magnitude in the time consumed by 
query processing.

% --------------------------------------------------------------------------------------------------------------------------------------------------------------------

% paper organization
%
In the following Section~\ref{c:description} we present the organization of 
multiset-trie data structure. The representation of multisets in multiset-trie is 
explained in detail.
%
In Section~\ref{c:operations} we present operations that multiset-trie currently 
supports. Those are the multiset containment and the basic search tree functions. 
The algorithms in pseudo code are presented as well. 
%
The description of multiset-trie functions and procedures is followed by the 
mathematical analysis of their complexity in Section~\ref{c:analysis}. 
We assume that multisets are constructed uniformly at random and are parametrized 
by several parameters, such as multiplicity and the alphabet. By using probabilistic 
tools we describe time complexity of the algorithms and space complexity of the structure.
%
Further, in Section~\ref{c:experiments} we present an empirical study of the 
multiset-trie. Artificially generated as well as real-world data sets are used in experiments. 
The experiments are dedicated to testing the performance of the data structure while 
varying selected parameters. The experiments also highlight the methods for optimizing a multiset-trie.
%
The Section~\ref{c:relwork} presents related work. The connection to the set-trie 
data structure \cite{savnik2013index} is discussed more explicitly. We also relate 
the multiset-trie to the information retrieval systems. In particular, we refer to the 
inverted index data structure and discuss how the multiset-trie can be used as a 
database index.
%
Finally, in Section~\ref{c:conclusions} our conclusion about the multiset-trie 
data structure and discussion of future work are presented.
